SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-03-01 scipy-1.0/paper.tex
ctypes/cffi should be teletype
Tightened LowLevelCallable section I removed details that, in my opinion, weakened the section. If these details are very important and can potentially strengthen the section, please let me know. Perhaps I just didn't understand. If that's the case, we can work together on how they are presented.

As of SciPy version 0.19, it is possible for users to wrap low-level functions
in a \texttt{scipy.LowLevelCallable} object that reduces the overhead of
calling compiled C functions directly from Python.  Supported low-level
functions include \texttt{PyCapsule} objects, ctypes function pointers, and
cffi function pointers. The low level function signature must be consistent
with the expectations of the routine it is passed to. For example, the
documentation for \texttt{scipy.ndimage.generic\_filter} defines two acceptable
C callback function signatures that may be used to produce functions that
operate on each element of image data with low overhead. The C code may be
generated using numba or Cython, for example, as long as the function call
signature matches the specifications. Furthermore, it is even possible to
generate a low-level callback function automatically from a Cython module using
\texttt{scipy.LowLevelCallable.from\_cython}.

>>>>

As of SciPy version 0.19, it is possible for users to wrap low-level functions
in a \texttt{scipy.LowLevelCallable} object that reduces the overhead of
calling compiled C functions directly from Python.  
Supported low-level functions include \texttt{PyCapsule} 
objects, \texttt{ctypes} function pointers, and \texttt{cffi} function pointers. 
Furthermore, it is even possible to generate a low-level callback function 
automatically from a Cython module using \texttt{scipy.LowLevelCallable.from\_cython}.
